Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
small fix + removed paragraph

As we shall show, the delayed check of contract, while essential to
ensuring that schema validation doesn't affect performance (or, indeed,
is possible at all on functions), make union contracts (and their less
appreciated sibling, intersection contracts) quite problematic.
While usual contracts require only one witness to show the invalidation
of a contract, the introduction of unions makes
the number of witnesses not constantly bounded.

@@

As a first obstacle, it's worth noting that their system is intended
to get stuck upon the checking of a contract in a context that shouldn't
be checked in, while to keep the semantics of unions and intersections
valid, we'd expect for that check to get skipped, and for execution
to continue.

>>>>

As we shall show, the delayed check of contract, while essential to
ensuring that schema validation doesn't affect performance (or, indeed,
is possible at all on functions), make union contracts (and their less
appreciated sibling, intersection contracts) quite problematic.
While usual contracts require only one witness to show the invalidation
of a contract, the introduction of unions makes
the number of witnesses not bounded.

@@

% As a first obstacle, it's worth noting that their system is intended
% to get stuck upon the checking of a contract in a context that shouldn't
% be checked in, while to keep the semantics of unions and intersections
% valid, we'd expect for that check to get skipped, and for execution
% to continue.
